### 2017-12-07 manuscript.rmd
fixed extended median depth contMap

 ```{r median_cont_BWincluded, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species including blue water diving observations."}
# median_aggregate = aggregate(trimmed_SDdata$Depth,by=list(trimmed_SDdata$Species), FUN=median)
# names(median_aggregate) = c("Spp","Depth")
# median_aggregate[33,2] = 0
# median_aggregate = median_aggregate[match(median_aggregate$Spp, ultratree$tip.label),]
# median_depth = median_aggregate$Depth
# names(median_depth) = median_aggregate$Spp
# depthmap <- contMap(ultratree, median_depth, plot=F) %>% setMap(colors=c("cyan","blue","black"))
# plot(depthmap)
```

>>>>

```{r median_depth_extended, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species including blue water diving observations." }

median_extended = cdata$Median.Depth.Extended
names(median_extended) = rownames(cdata)
median_extended = median_extended[match(names(median_extended), ultratree$tip.label),]
depthmap_ext <- contMap(ultratree, median_extended, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap_ext)
